\Title

### 2023-02-20 cover_letter/2023-02-20_coverletter.tex
cover_letter
Update on Overleaf.

@@

 \noteRev{The main differences with the previous study are in the task to solve (section 2.1) and in the analysis of the results. The response of the model is tested on different sets of motion cloud stimuli with a control of the parameters of such stimuli generation (section 3.2). Regarding the MLR model, main differences with the previous ones are reported in the methods (P8, L269).}

@@

 \noteRev{We improved the mathematical formulation of the model in sections 2.2.1 and 2.2.2 and hope that it clarifies the general framework we use. Regarding training, it is described more clearly in P8, L295. Demonstration of the mechanism and the analogy with Hebbian learning was done in~\cite{grimaldi_robust_2022} and was not reproduced here. We hope this new version offers a clearer methodology.}

@@

 \noteRev{We gave a better explanation of the symmetry assumption in the methods (P8, L293) an how this new model uses this invariance in its computation like observed in complex cells. Indded, we don't want the polarity to have an impact on the classification and then this observation does not apply to the revised manuscript as it is a prior and not an emergent property.}

@@

\noteRev{In fact, there was no mention of this previous work in the original manuscript, as this 4-page paper had not yet been published in the proceedings of the conference at which it had been presented. As mentioned in the responses to reviewer \#1 in this cover letter, we have now added this citation~\cite{grimaldi_learning_2022}. In addition, in this submitted manuscript we describe the main differences from that previous study: the use of a more ecological task (Section 2.1), a complete formulation of the model (Section 2.2), and the improvements made in this particular model (P8, L269). We also provide citations to studies using similar methods (P7, L243). Further results are presented, especially the testing of the learned model with parametric textures.}

\bibliographystyle{apalike}
\bibliography{../FastMotionDetection}

>>>>

\usepackage{natbib}

@@

 \noteRev{The main differences with the previous study are in the task to solve (section 2.1) and in the analysis of the results. The response of the model is tested on different sets of motion cloud stimuli with a control of the parameters of such stimuli generation (section 3.2). Regarding the MLR model, main differences with the previous ones are reported in the methods (P8, L285).}

@@

 \noteRev{We improved the mathematical formulation of the model in sections 2.2.1 and 2.2.2 and hope that it clarifies the general framework we use. Regarding training, it is described more clearly in P9, L313. Demonstration of the mechanism and the analogy with Hebbian learning was done in~\cite{grimaldi_robust_2022} and was not reproduced here. We hope this new version offers a clearer methodology.}

@@

 \noteRev{We gave a better explanation of the symmetry assumption in the methods (P9, L303) an how this new model uses this invariance in its computation like observed in complex cells. Indded, we don't want the polarity to have an impact on the classification and then this observation does not apply to the revised manuscript as it is a prior and not an emergent property.}

@@

\noteRev{In fact, there was no mention of this previous work in the original manuscript, as this 4-page paper had not yet been published in the proceedings of the conference at which it had been presented. As mentioned in the responses to reviewer \#1 in this cover letter, we have now added this citation~\cite{grimaldi_learning_2022}. In addition, in this submitted manuscript we describe the main differences from that previous study: the use of a more ecological task (Section 2.1), a complete formulation of the model (Section 2.2), and the improvements made in this particular model (P8, L285). We also provide citations to studies using similar methods (P8, L259). Further results are presented, especially the testing of the learned model with parametric textures.}

\bibliographystyle{plainnat}
\bibliography{FastMotionDetection}
